Multimodal Corpora

### 2016-12-25 paper.tex
Add first outline; Add specific outline for third corpus; Add todos
Add intro to SaGA; Add glossary

\usepackage{graphicx}
\usepackage{amssymb,amsmath,bm}
\usepackage{textcomp}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If multiple authors, uncomment and edit the lines shown below.       %%
%% Note that each line must be emphasized {\em } by itself.             %%
%% (by Stephen Martucci, author of spconf.sty).                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother
\name{{\em Tuan Pham Minh, Nils Harder, Tilman Krokotsch}}
%%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%

\address{Otto-von-Guericke-University Magdeburg \\
  Faculty of Computer Science \\
  Faculty of Electrical Engineering and Information Technology \\
  {\small \tt \{tuan.pham, nils.harder, tilman.krokotsch\}@st.ovgu.de}
}

@@

  \section{Introduction}

>>>>

\usepackage{graphicx}
\usepackage{amssymb,amsmath,bm}
\usepackage{textcomp}
\usepackage{todo}
\usepackage{glossaries}

@@

% Authors
\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother
\name{{\em Tuan Pham Minh, Nils Harder, Tilman Krokotsch}}

% Affilations and Contact information
\address{Otto-von-Guericke-University Magdeburg \\
  Faculty of Computer Science \\
  Faculty of Electrical Engineering and Information Technology \\
  {\small \tt \{tuan.pham, nils.harder, tilman.krokotsch\}@st.ovgu.de}
}

%Acronyms
\newacronym{saga}{SaGA}{Bielefeld Speech and Gesture Alignment Corpus}
\newacronym{dfg}{DFG}{German Research Foundation}
\newacronym{lrec}{LREC}{Language Resources and Evaluation Conference}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  	\section{Introduction}
		\Todo{Add definitions and intro to multimodal corpora}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\section{First Corpus}
		\Todo{Add first corpus}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\section{Second Corpus}
		\Todo{Add second corpus}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\section{The Bielefeld Speech and Gesture Alignment Corpus ( SaGA )}
		The \gls{saga} was produced by a research group at the University of Bielefeld and funded by the \gls{dfg}. It was carried out in the CRC 673 "Alignment in Communication" and published in the proceedings of the workshop "Multimodal Corpora-Advances in Capturing, Coding and Analyzing Multimodality" at the \gls{lrec} in 2010 \cite{Bielefeld2010}.

		The aim of the corpus was to portray the interplay of speech and gesture in face to face conversations. This task was taken on by a interdisicplinary approach. On the one hand the research team took a linguistic perspective to enable Theoretical Linguistic Reconstructions based on the corpus data, and on the other hand took the perspective of computer science to implement the lingusistic findings for multimodal communication in virtual agents and robots. \cite[Ch. 1]{Bielefeld2010}

		\subsection{Recording Scenario}

		\subsection{Recorded Data}
			\subsubsection{Primary Data}

			\subsubsection{Secondary Data}

		\subsection{Evaluation}

		\subsection{Application}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
